### 2020-08-14 _meta/templates/Abstract_&_Setup.Rmd
refactor

<EN>abstract:
 Compressive strength is the main characteristic of concrete. The correct prediction of this parameter means cost and time reduction. This work built predictive models for 6 different ages of concrete samples (3, 7, 14, 28, 56, and 100 days). A set of data obtained in previous studies was used, a total of 1030 samples, with 9 variables: resistance to compression, age, and 7 ingredients (water, cement, fine aggregate, coarse aggregate, fly ash, blast furnace slag, and superplasticizers). Another 6 variables were added to represent the proportions of the main ingredients in each sample (water/cement, fine aggregate/cement, coarse aggregate/cement, fine aggregate/coarse aggregate, water/coarse aggregate, and water/fine aggregate). The predictive models were developed in *R* language, using the *caret* package with the *Parallel Random Forest* algorithm and repeated cross-validation technique to optimize the parameters. The results were satisfactory and compatible with other studies using the same data set. The most important model, 28 days old, obtained *RMSE* of 4.717. The 3-day model obtained the best result, *RMSE* of 3.310. The worst result was the 56-day model, with *RMSE* of 5.939. The work showed that the compressive strength of concrete can be predicted. The choice of creating a model for each age, instead of using age as a predictor, allowed to get compatible results with the available data at each age. It was a promising alternative since good results were achieved by training with just one algorithm. This work facilitates exploration and new efforts to predict the compressive strength of concrete, it can be replicated using different algorithms or the combination of several.</EN>
<PT>abstract:
  A resistência à compressão é a principal característica do concreto. A previsão correta desse parâmetro significa redução de custo e tempo. Esse trabalho construiu modelos de previsão em 6 idades diferentes de amostras de concreto (3, 7, 14, 28, 56, e 100 dias). Foi utilizado um conjunto de dados obtido em estudos anteriores, um total de 1030 amostras, com 9 variáveis: resistência à compressão, idade e 7 ingredientes (água, cimento, agregado miúdo, agregado graúdo, cinza volante, escória granulada de alto forno e superplastificantes). Outras 6 variáveis foram adicionadas para representar as proporções dos principais ingredientes em cada amostra (água/cimento, agregado miúdo/cimento, agregado graúdo/cimento, agregado miúdo/agregado graúdo, água/agregado graúdo e água/agregado miúdo). Os modelos de previsão foram desenvolvidos em linguagem *R*, utilizando o pacote *caret* com o algoritmo *Parallel Random Forest* e técnica de validação cruzada repetida para otimização dos parâmetros. Os resultados foram satisfatórios e compatíveis com outros estudos utilizando o mesmo conjunto de dados. O modelo mais importante, de 28 dias, obteve *RMSE* de 4,717. O modelo de 3 dias obteve o melhor resultado, *RMSE* de 3,310. O pior resultado foi o modelo de 56 dias, com *RMSE* de 5,939. O trabalho mostrou que a resistência à compressão do concreto pode ser prevista. A escolha de criar um modelo para cada idade, ao invés de utilizar a idade como característica para previsão, permitiu chegar a resultados compatíveis com os dados disponíveis de cada idade. Foi uma alternativa promissora, visto que bons resultados foram atingidos treinando com apenas um algoritmo. Esse trabalho facilita a exploração e novos esforços para previsão da resistência à compressão do concreto, ele pode ser replicado utilizando diferentes algoritmos ou a combinação de diversos.</PT>

>>>>

<EN>abstract: "Compressive strength is the main characteristic of concrete. The correct prediction of this parameter means cost and time reduction. This work built predictive models for 6 different ages of concrete samples (3, 7, 14, 28, 56, and 100 days). A set of data obtained in previous studies was used, a total of 1030 samples, with 9 variables: compressive strength, age, and 7 ingredients (water, cement, fine aggregate, coarse aggregate, fly ash, blast furnace slag, and superplasticizers). Another 6 variables were added to represent the proportions of the main ingredients in each sample (water/cement, fine aggregate/cement, coarse aggregate/cement, fine aggregate/coarse aggregate, water/coarse aggregate, and water/fine aggregate). The predictive models were developed in *R* language, using the *caret* package with the *Parallel Random Forest* algorithm and repeated cross-validation technique to optimize the parameters. The results were satisfactory and compatible with other studies using the same data set. The most important model, 28 days old, obtained *RMSE* of 4.717. The 3-day model obtained the best result, *RMSE* of 3.310. The worst result was the 56-day model, with *RMSE* of 5.939. The work showed that the compressive strength of concrete can be predicted. The choice of creating a model for each age, instead of using age as a predictor, allowed to get compatible results with the available data at each age. It was a promising alternative since good results were achieved by training with just one algorithm. This work facilitates exploration and new efforts to predict the compressive strength of concrete, it can be replicated using different algorithms or the combination of several."</EN>
<PT>abstract: "A resistência à compressão é a principal característica do concreto. A previsão correta desse parâmetro significa redução de custo e tempo. Esse trabalho construiu modelos de previsão em 6 idades diferentes de amostras de concreto (3, 7, 14, 28, 56, e 100 dias). Foi utilizado um conjunto de dados obtido em estudos anteriores, um total de 1030 amostras, com 9 variáveis: resistência à compressão, idade e 7 ingredientes (água, cimento, agregado miúdo, agregado graúdo, cinza volante, escória granulada de alto forno e superplastificantes). Outras 6 variáveis foram adicionadas para representar as proporções dos principais ingredientes em cada amostra (água/cimento, agregado miúdo/cimento, agregado graúdo/cimento, agregado miúdo/agregado graúdo, água/agregado graúdo e água/agregado miúdo). Os modelos de previsão foram desenvolvidos em linguagem *R*, utilizando o pacote *caret* com o algoritmo *Parallel Random Forest* e técnica de validação cruzada repetida para otimização dos parâmetros. Os resultados foram satisfatórios e compatíveis com outros estudos utilizando o mesmo conjunto de dados. O modelo mais importante, de 28 dias, obteve *RMSE* de 4,717. O modelo de 3 dias obteve o melhor resultado, *RMSE* de 3,310. O pior resultado foi o modelo de 56 dias, com *RMSE* de 5,939. O trabalho mostrou que a resistência à compressão do concreto pode ser prevista. A escolha de criar um modelo para cada idade, ao invés de utilizar a idade como característica para previsão, permitiu chegar a resultados compatíveis com os dados disponíveis de cada idade. Foi uma alternativa promissora, visto que bons resultados foram atingidos treinando com apenas um algoritmo. Esse trabalho facilita a exploração e novos esforços para previsão da resistência à compressão do concreto, ele pode ser replicado utilizando diferentes algoritmos ou a combinação de diversos."</PT>
